My title

### 2022-02-06 outputs/paper/paper.Rmd
commiting again

On December 31, 2019 the world saw its first case of the coronavirus, officially referred to as SARS-CoV-2 or COVID-19, in Wuhan China and by January 25, 2020 Toronto had seen its first case. Ever since, the virus continues to spread in various forms like the Delta variant and the most recent being the Omicron variant. The province has taken many attempts at fighting the virus which include locking down the province and shutting down non-essential activities in hopes of limiting close contact between citizens.

>>>>

On December 31, 2019 the world saw its first case of the coronavirus, officially referred to as SARS-CoV-2 or COVID-19, in Wuhan China and by January 25, 2020 Toronto had seen its first case. Ever since, the virus continues to spread in various forms like the Delta variant and the most recent being the Omicron variant. The province has taken many attempts at fighting the virus which include locking down the province and shutting down non-essential activities in hopes of limiting close contact between citizens. Even constant advancements in vaccines are not able to completely fight the virus, whether that be Pfizer, Moderna or AstraZeneca.

With how quickly the virus is spreading, it is important that we analyze data that has been collected over the past two years and see if there are any trends and patterns that are visible that can better prepare the city for any newer variants. Using the data given to us from Open Data Toronto, we can begin to determine what factors play a role in increasing the number of cases of covid. These factors could be the time of the year or general age of the population or one can learn which source of infection is most common so that they can take the necessary actions to ensure that they remain safe. When analyzing this data it is also important to take context into account. This includes things like when new variants came to light, when vaccines were introduced and why one could be noticing a certain trend at a certain time of the month. One can only obtain a better understanding of the data when context of the data is also given importance to. (add more)
